RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-21 main.tex
:pencil: Updating related works

	\gls{sr} incorporates a passive scatterer into existing radio networks to create additional propagation path and ride its own information for the cooperative receiver.

@@

	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source for heterogeneous traffic control and universal hardware design.

@@

	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form.
	We show RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.

@@

	% For a typical scenario

@@

	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transit between backscatter modulation and passive beamforming via smart input distribution design.

@@

@@

		As an emerging low-power communication technique, \gls{bc} divides conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.

@@

		To tackle this, \cite{Liu2013b} proposed an \gls{ambc} system where interactive nodes recycle ambient legacy signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections, as shown in Fig. \subref*{fg:ambc}.

@@

		The concept of cooperative \gls{ambc} was further refined as \gls{sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}, which in shown Fig. \subref*{fg:sr}.

@@

		In \gls{sr}, the active transmitter generates \gls{rf} wave carrying primary information, the passive node enhances the propagation environment and superimposes its own message on the scattered signal, and the cooperative receiver jointly or sequentially decodes both links.

@@

		The reflection pattern over time is deterministic, which can be optimized and reported to the user before transmission.

@@

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                               & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                       & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                     & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                       & ---                       & No                                              & Active beamforming                           & ---                                     & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                     & Backscatter detection as primary channel training \\ \midrule
			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                & Coherent                                          \\ \midrule
			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                     & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)         & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

	\begin{subsection}{Related Works}
		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
		To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
		% However, it assumed equal symbol period of both links with perfect synchronization, which is impractical due to the load-switching speed constraint.
		% However, it assumed the primary and backscatter symbol periods are equal and
		% However, it only considered the case where primary and backscatter symbols have the same period.
		However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
		Joint \gls{ml} decoding can achieve the best error performance in general, but its computational complexity is prohibitive especially for nodes with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
		One special property of \gls{sr} is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential primary-backscatter decoding with \gls{sic}.
		During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between primary sampling rate and backscatter switching speed.
		If the former is much higher, then the average primary achievable rate under noncoherent detection would approach its coherent counterpart asymptotically \cite{Long2020a}, and both links may be decoded in an interference-free manner.
		% For sequential primary-backscatter decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio \cite{Long2020a}.
		% If this ratio is sufficiently large, the authors proved the noncoherent primary achievable rate would approach its coherent counterpart asymptotically.
		% This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to perform \gls{sic} from primary to backscatter links.
		However, the disadvantage of such \gls{sic} includes:
		1) primary rate analysis is backed by long backscatter symbol period that constrains backscatter rate;
		2) reflection pattern and signal characteristics are not fully exploited;
		3) noncoherent primary encoding is required at the transmitter while re-encoding, precoding and subtraction are required at the receiver;
		4) primary and backscatter symbols are superimposed by multiplication instead of superposition.

>>>>

	\gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.

@@

	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.

@@

	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for universal hardware design and heterogeneous traffic control.
	% ? We show RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.

@@

@@

	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design,

@@

	and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in scatter-based cooperative networks.
	% with low complexity.

@@

		As a mature low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.

@@

		To tackle this, \cite{Liu2013b} proposed an \gls{ambc} system where interactive nodes recycle ambient legacy signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections, and the idea is shown in Fig. \subref*{fg:ambc}.

@@

		The concept of cooperative \gls{ambc} was further refined as \gls{sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}, as shown in Fig. \subref*{fg:sr}.

@@

		In \gls{sr}, the active transmitter generates \gls{rf} wave carrying primary information, the passive node enhances the radio propagation and superimposes its own message on the scattered signal, and the cooperative receiver jointly or sequentially decodes both links.

@@

		The reflection pattern is deterministic over time, which can be optimized and reported to the user before the transmission.

@@

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                                  & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                          & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmissions     & ---                       & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\ \midrule
			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                   & Coherent                                          \\ \midrule
			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

	\begin{subsection}{Related Works}
		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
		To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
		% However, it assumed equal symbol period of both links with perfect synchronization, which is impractical due to the load-switching speed constraint.
		% However, it assumed the primary and backscatter symbol periods are equal and
		% However, it only considered the case where primary and backscatter symbols have the same period.
		However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
		Joint \gls{ml} decoding achieves the best error performance in general, but its computational complexity can be prohibitive especially for sources with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
		One special property of scatter-based cooperative networks is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential \gls{sic}-based primary-backscatter decoding.
		During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between the primary sampling rate and backscatter switching speed.
		% During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between backscatter switching speed and primary sampling rate.
		% If the backscatter-over-primary symbol period ratio $N$ is sufficiently large (i.e., commensal \gls{sr}), then the average primary achievable rate under noncoherent detection would asymptotically approach its coherent counterpart \cite{Long2020a}, and both links may be decoded in an interference-free manner.
		If the former is much higher (i.e., commensal \gls{sr}), then the average primary achievable rate under noncoherent detection would asymptotically approach its coherent counterpart \cite{Long2020a}, and both links may be decoded in an interference-free manner.
		% For sequential primary-backscatter decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio \cite{Long2020a}.
		% If this ratio is sufficiently large, the authors proved the noncoherent primary achievable rate would approach its coherent counterpart asymptotically.
		% This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to perform \gls{sic} from primary to backscatter links.
		% However, the disadvantage of \gls{sic}-based sequential detection includes:
		% 1) the achievable primary and backscatter rate analysis for commensal \gls{sr} only holds for a sufficiently large $N$;
		% 1) the asymptotic rate analysis for commensal \gls{sr} is inapplicable when primary and backscatter symbol periods are comparable; \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio between \num{1} and \num{100}.}
		% ! However, the disadvantage of \gls{sic}-based sequential detection includes:
		% 1) the asymptotic rate analysis for commensal \gls{sr} is inapplicable when symbol periods are comparable \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio between \num{1} and \num{100}.};
		% 2) using a large symbol period ratio not only reduces backscatter throughput, but also requires \gls{sic} over every primary block
		However, it requires \gls{sic} over all primary symbol blocks followed by a time-domain \gls{mrc}, which is
		% computationally expensive
		operation-intensive and \gls{csi}-sensitive.
		Besides, the assumption of very large backscatter-over-primary symbol period ratio not always hold in modern wireless systems \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio between \num{1} and \num{100}.}.

		% the assumption of long backscatter symbol constrains the backscatter data rate\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical (backscatter-over-primary) symbol period ratio between \num{1} and \num{100}.}

		% First, we observe both \gls{bbc} and \gls{sr} can achieve the highest backscatter rate with coherent detection over the receive energy and intermediate signal, respectively.
		% This is because repetition coding with \gls{mrc} over $N$ primary blocks effectively increases the backscatter \gls{snr} by $N$ times, and the information loss due to the signal-to-energy conversion on top may be insignificant.
		% However, the asymptotic primary and backscatter rate analysis only provides upper bounds for \gls{sr}.
		% Using a very large $N$ not only reduces the system throughput\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio $N$ between \num{1} and \num{100}.} but also requires the operation-intensive \gls{sic} over each primary block.
		% When the duration of primary and backscatter symbol are comparable, the randomly scattered signals should be modelled as interference to primary link rather than quasi-static multipath components, and the achievable rate point of \gls{sr} will move towards the origin.

		primary rate analysis is backed by long backscatter symbol period that constrains backscatter rate;
		2) reflection pattern and signal characteristics are not fully exploited;
		3) noncoherent primary encoding is required at the transmitter while re-encoding, precoding and subtraction are required at the receiver;
		4) primary and backscatter symbols are superimposed by multiplication instead of superposition.
